\begin{thebibliography}{99}\small

\bibitem[Belinkov(2022)]{r_belinkov}
Yonatan Belinkov.
\newblock Probing classifiers: Promises, shortcomings, and advances.
\newblock \emph{Computational Linguistics}, 48(1), 2022.

\bibitem[Chi et al.(2023)]{r_diffusionpolicy}
Cheng Chi, Zhenjia Xu, Siyuan Feng, Eric Cousineau, Yilun Du, Benjamin Burchfiel, Russ Tedrake, and Shuran Song.
\newblock Diffusion policy: Visuomotor policy learning via action diffusion.
\newblock \emph{Robotics: Science and Systems}, 2023.

\bibitem[Deng et al.(2023)]{r_s4wm}
Fei Deng, Junyoung Park, and Sungjin Ahn.
\newblock Facing off world model backbones: RNNs, transformers, and S4.
\newblock \emph{NeurIPS}, 2023.

\bibitem[Gao \& Xu(2026)]{r_fastlewm}
Yuntian Gao and Xiangyu Xu.
\newblock Fast LeWorldModel.
\newblock arXiv:2606.26217, 2026.

\bibitem[Hafner et al.(2025)]{r_dreamerv3}
Danijar Hafner, Jurgis Pasukonis, Jimmy Ba, and Timothy Lillicrap.
\newblock Mastering diverse control tasks through world models.
\newblock \emph{Nature}, 640:647--653, 2025.

\bibitem[Laird \& Clark(2025)]{r_onmemory}
Eli J. Laird and Corey Clark.
\newblock On memory: A comparison of memory mechanisms in world models.
\newblock arXiv:2512.06983, 2025.

\bibitem[Li et al.(2026)]{r_rcaux}
Wenyuan Li, Guang Li, Keisuke Maeda, Takahiro Ogawa, and Miki Haseyama.
\newblock Predictive but not plannable: RC-aux for latent world models.
\newblock arXiv:2605.07278, 2026.

\bibitem[Maes et al.(2026)]{r_lewm}
Lucas Maes, Quentin Le Lidec, Damien Scieur, Yann LeCun, and Randall Balestriero.
\newblock LeWorldModel: Stable end-to-end joint-embedding predictive architecture from pixels.
\newblock arXiv:2603.19312, 2026.

\bibitem[Ravichander et al.(2021)]{r_ravich}
Abhilasha Ravichander, Yonatan Belinkov, and Eduard Hovy.
\newblock Probing the probing paradigm: Does probing accuracy entail task relevance?
\newblock \emph{EACL}, 2021.

\bibitem[Samsami et al.(2024)]{r_r2i}
Mohammad Reza Samsami, Artem Zholus, Janarthanan Rajendran, and Sarath Chandar.
\newblock Mastering memory tasks with world models.
\newblock \emph{ICLR}, 2024.

\bibitem[Zheng et al.(2026)]{r_memworld}
Zirui Zheng, Jiaqian Yu, Xiongfeng Peng, Jun Shi, Mingyi Li, Chao Zhang, Weiming Li, Dong Wang, Huchuan Lu, and Xu Jia.
\newblock Mem-World: Memory-augmented action-conditioned world models for persistent robot manipulation.
\newblock arXiv:2606.18960, 2026.

\bibitem[Zhou et al.(2025)]{r_dinowm}
Gaoyue Zhou, Hengkai Pan, Yann LeCun, and Lerrel Pinto.
\newblock DINO-WM: World models on pre-trained visual features enable zero-shot planning.
\newblock \emph{ICML}, 2025.

\end{thebibliography}
