\bibliographystyle{plainnat}
\begin{thebibliography}{99}
\setlength{\itemsep}{-0.5pt}

\bibitem[Assran et~al.(2023)]{r_jepa}
Mahmoud Assran, Quentin Duval, Ishan Misra, Piotr Bojanowski, Pascal Vincent,
Michael Rabbat, Yann LeCun, and Nicolas Ballas.
\newblock Self-supervised learning from images with a joint-embedding predictive architecture.
\newblock In \emph{CVPR}, 2023.

\bibitem[Zhou et~al.(2025)]{r_dinowm}
Gaoyue Zhou, Hengkai Pan, Yann LeCun, and Lerrel Pinto.
\newblock DINO-WM: World models on pre-trained visual features enable zero-shot planning.
\newblock In \emph{ICML}, 2025.

\bibitem[Maes et~al.(2026)]{r_lewm}
Lucas Maes, Quentin Le Lidec, Damien Scieur, Yann LeCun, and Randall Balestriero.
\newblock LeWorldModel: Stable end-to-end joint-embedding predictive architecture from pixels.
\newblock \emph{arXiv:2603.19312}, 2026.

\bibitem[Anonymous(2026)]{r_causaljepa}
Anonymous.
\newblock Causal-JEPA: Learning world models through object-level latent masking.
\newblock \emph{arXiv:2602.11389}, 2026.

\bibitem[Cho et~al.(2014)]{r_gru}
Kyunghyun Cho, Bart van Merrienboer, Caglar Gulcehre, Dzmitry Bahdanau,
Fethi Bougares, Holger Schwenk, and Yoshua Bengio.
\newblock Learning phrase representations using RNN encoder-decoder for statistical machine translation.
\newblock In \emph{EMNLP}, 2014.

\bibitem[Hochreiter and Schmidhuber(1997)]{r_lstm}
Sepp Hochreiter and J{\"u}rgen Schmidhuber.
\newblock Long short-term memory.
\newblock \emph{Neural Computation}, 9(8):1735--1780, 1997.

\bibitem[Gu and Dao(2023)]{r_mamba}
Albert Gu and Tri Dao.
\newblock Mamba: Linear-time sequence modeling with selective state spaces.
\newblock \emph{arXiv:2312.00752}, 2023.

\bibitem[Jiang et~al.(2024)]{r_slotssm}
Jindong Jiang, Fei Deng, Gautam Singh, Minseung Lee, and Sungjin Ahn.
\newblock Slot state space models.
\newblock In \emph{NeurIPS}, 2024.

\bibitem[Zhang et~al.(2024)]{r_gsa}
Yu Zhang et~al.
\newblock Gated slot attention for efficient linear-time sequence modeling.
\newblock In \emph{NeurIPS}, 2024.

\bibitem[Anonymous(2026)]{r_slotmemory}
Anonymous.
\newblock SlotMemory: Object-centric KV memory for streaming long-video generation.
\newblock \emph{arXiv:2605.31033}, 2026.

\bibitem[Behrouz et~al.(2025)]{r_titans}
Ali Behrouz, Peilin Zhong, and Vahab Mirrokni.
\newblock Titans: Learning to memorize at test time.
\newblock \emph{arXiv:2501.00663}, 2025.

\bibitem[Sun et~al.(2024)]{r_ttt}
Yu Sun et~al.
\newblock Learning to (learn at test time): RNNs with expressive hidden states.
\newblock \emph{arXiv:2407.04620}, 2024.

\bibitem[Hsieh et~al.(2024)]{r_ruler}
Cheng-Ping Hsieh, Simeng Sun, Samuel Kriman, Shantanu Acharya, Dima Rekesh,
Fei Jia, Yang Zhang, and Boris Ginsburg.
\newblock RULER: What's the real context size of your long-context language models?
\newblock In \emph{COLM}, 2024.

\bibitem[Wu et~al.(2025)]{r_longmemeval}
Di Wu, Hongwei Wang, Wenhao Yu, Yuwei Zhang, Kai-Wei Chang, and Dong Yu.
\newblock LongMemEval: Benchmarking chat assistants on long-term interactive memory.
\newblock In \emph{ICLR}, 2025.

\bibitem[Laird and Clark(2025)]{r_onmemory}
Eli J. Laird and Corey Clark.
\newblock On memory: A comparison of memory mechanisms in world models.
\newblock \emph{arXiv:2512.06983}, 2025.

\bibitem[Rao and Ballard(1999)]{r_predictivecoding}
Rajesh P. N. Rao and Dana H. Ballard.
\newblock Predictive coding in the visual cortex: A functional interpretation
of some extra-classical receptive-field effects.
\newblock \emph{Nature Neuroscience}, 2:79--87, 1999.

\bibitem[Friston et~al.(2017)]{r_activeinference}
Karl Friston, Thomas FitzGerald, Francesco Rigoli, Philipp Schwartenbeck, and
Giovanni Pezzulo.
\newblock Active inference: A process theory.
\newblock \emph{Neural Computation}, 29(1):1--49, 2017.

\bibitem[Ahuja et~al.(2023)]{r_interventionalcrl}
Kartik Ahuja, Yixin Wang, Divyat Mahajan, and Yoshua Bengio.
\newblock Interventional causal representation learning.
\newblock In \emph{ICML}, 2023.

\end{thebibliography}
