Finite-context world models can observe a decisive visual cue and later act as
if it was never seen.  We treat this as an interface problem rather than an
architecture label: old evidence must survive beyond the legal context window
and must also be exposed through a frozen host representation in a form a later
consumer can use.  A valid memory claim must therefore separate four questions:
whether the cue lies outside the legal window, whether it is retained after the
window expires, whether the frozen interface exposes it, and whether a bounded
controller can act on it.  We instantiate this ladder with a self-supervised
masked-evidence JEPA objective and a compact slot-memory writer.  Training never
sees cue labels, cue crops, or key-frame annotations; salient patch sets are
mined from the rendered stream, withheld from the visible context, and predicted
from a causal memory state, while cue labels enter only afterwards for a
fail-closed audit under matched full, reset, and no-state conditions.  Across a
suite of OGBench render decks, controlled evidence ages, and seeds, the slot
interface clears every registered retention gate while matched controls stay at
chance, and the largest margins over recurrent GRU, LSTM, and Mamba-lite writers
appear exactly where evidence is old or spread across object-like structure.
Trained on delays sampled continuously (log-uniform) over the legal range, the
same interface retains and exposes old evidence smoothly across the whole delay
axis rather than at a few fixed ages, and we summarize retention with general,
age-agnostic metrics (maximum passing delay and retention AUC) instead of
per-age tables; the memory is bounded in output throughout, and a streaming
variant that evicts
old tokens additionally bounds the attention context, scaling to far longer
horizons at constant per-step memory and compute.  The
advantage survives matching the carrier capacity and adding structured
state-space, gated-slot, and retrieval memories, does not depend on a colour
shortcut when the cue identity is decorrelated from colour, and transfers into a
frozen LeWorldModel host, where the injected memory exposes old evidence in the
host's own predictive output beyond its context window.  The contribution is a
scoped audit-and-method result: persistent old-evidence memory in latent world
models is a property of the target--carrier--host--consumer interface, not a
universal property of any single recurrent or state-space module.
