\section{Artifact map and reproducibility}
\label{app:artifacts}

The paper is generated from local JSON/NPZ artifacts and does not hand-enter the
main numbers.  The generator is \path{scripts/plot_paper_c.py}; it writes
figures to \path{paper_c/figures/}, tables to
\path{paper_c/generated_results/}, and a machine-readable snapshot to
\path{paper_c/generated_results/result_snapshot.json}.  Every table and figure
below is a deterministic function of the source summaries in
Table~\ref{tab:sources}.

\begin{table}[h]
\centering
\footnotesize
\caption{Local result sources for every table and figure, grouped by protocol
(P0--P3) and revision analysis.}
\label{tab:sources}
\begin{tabularx}{\linewidth}{lYl}
\toprule
Claim & Local source & Figure / table\\
\midrule
Slot-memory main audit (P0)
  & \path{outputs/multiview_patchset_color_jepa_native_v1/summary.json}
  & Tab.~\ref{tab:main-comparison},~\ref{tab:delay-summary},~\ref{tab:env-retention-summary}; Fig.~\ref{fig:baseline-comparison}\\
GRU baseline
  & \path{outputs/memory_arch_baselines_v1/gru/summary.json}
  & Tab.~\ref{tab:main-comparison}\\
LSTM baseline
  & \path{outputs/memory_arch_baselines_v1/lstm/summary.json}
  & Tab.~\ref{tab:main-comparison}\\
Mamba-lite baseline
  & \path{outputs/memory_arch_baselines_v1/mamba_lite/summary.json}
  & Tab.~\ref{tab:main-comparison}\\
Fixed-controller native use (P0)
  & \path{outputs/native_use_repaired_combined_v2/\{stats,summary\}.json}
  & Tab.~\ref{tab:native-use},~\ref{tab:native-full}; Fig.~\ref{fig:native-use}\\
Continuous delay sweep (primary)
  & \path{outputs/paper_c_continuous_v1}
  & Tab.~\ref{tab:retention-summary}; Fig.~\ref{fig:continuous-retention}\\
Dense delay interpolation (P1)
  & \path{outputs/multiview_patchset_auto_age_v1}
  & Tab.~\ref{tab:delay-summary},~\ref{tab:env-retention-summary}; Fig.~\ref{fig:age-gen},~\ref{fig:env-heatmaps}\\
Long-horizon extrapolation (P2)
  & \path{outputs/paper_c_agescale_v1}
  & Tab.~\ref{tab:max-delay}; Fig.~\ref{fig:age-scaling}\\
Streaming cost profiling
  & \path{outputs/streaming_cost_v1/streaming_cost.json}
  & Fig.~\ref{fig:streaming-cost}\\
Capacity-matched + structured (P3)
  & \path{outputs/paper_c_revision_v1/stream_age15_s0}
  & Tab.~\ref{tab:structured},~\ref{tab:headline-recon}; Fig.~\ref{fig:capacity}\\
Bounded-streaming headline
  & \path{outputs/paper_c_revision_v1/stream_headline}
  & Tab.~\ref{tab:stream-headline}\\
Carrier / loss ablations
  & \path{outputs/paper_c_revision_v1/ablations}
  & Tab.~\ref{tab:abl-slots},~\ref{tab:abl-loss},~\ref{tab:headline-recon}\\
Shortcut-broken identity (P3)
  & \path{outputs/paper_c_revision_v1/shortcut_shape_age15_s0}
  & Fig.~\ref{fig:shortcut}\\
Attention + causal necessity
  & \path{outputs/evidence_discovery_v1/\{evidence_discovery,causal_evidence\}.json}
  & Fig.~\ref{fig:evidence},~\ref{fig:causal-evidence}\\
Frozen-LeWM host exposure
  & \path{outputs/lewm_pusht_host_writer_counterfactual_checkpointed_v1/summary.json}
  & Fig.~\ref{fig:lewm}\\
Frozen-LeWM control battery
  & \path{outputs/lewm_host_controls_v1/controls.json}
  & Tab.~\ref{tab:c-lewm-controls}; Fig.~\ref{fig:c-lewm-controls}\\
\bottomrule
\end{tabularx}
\end{table}

Each seed cell stores per-condition balanced accuracies and the confusion
matrices used in Figure~\ref{fig:cue-inference};
the shortcut-diagnostic panels (Figure~\ref{fig:cue-inference}) are refit at plot
time with a ridge readout on the stored train features to demonstrate that the
audit is reproducible from the raw feature banks (\path{features.npz}) rather
than from cached scores.

\section{Training and audit details}
\label{app:training}

All methods share the same rendered caches, validation split, target mining,
prediction head, and readout protocol.  Only the memory writer changes.
Table~\ref{tab:hyperparams} lists the hyperparameters.

\begin{table}[h]
\centering
\footnotesize
\caption{Shared training and evaluation hyperparameters.}
\label{tab:hyperparams}
\input{generated_results/appendix_hyperparams.tex}
\end{table}

\paragraph{Target miner.}
The causal history $[0,t]$ is split into $V{=}3$ contiguous temporal bins.  Per
bin, view saliency combines local color contrast with novelty against a running
mean of previously seen frames; one view is sampled per bin with probability
proportional to saliency, and the top-saliency patches from that view form the
target set.  The mined views are then removed from the visible token sequence so
the writer cannot copy the answer from a legal frame.  The miner uses no cue
labels, cue positions, or object crops; it is a generic visual saliency process.

\paragraph{Target encoder $\phi$.}
$\phi$ applies a $4{\times}4$ adaptive average pool, subtracts the per-patch
mean, appends a max$-$min saturation channel, and projects the result through a
fixed random matrix with a frozen seed.  Because $\phi$ is fixed and generic,
targets carry color/texture structure but not a semantic class, which is what
makes label-free training an honest test of retention.

\paragraph{Gate semantics.}
A seed cell passes when full-memory balanced accuracy is at least $0.750$ and
both reset and no-state controls are at most $0.350$ (Eq.~\eqref{eq:gate}).  An
environment-age row is all-pass only when all three seeds pass.  We also report
seed-pass counts (Appendix~\ref{app:full}) because they show partial stability
even where a row narrowly misses the strict all-pass criterion.

\paragraph{Baseline implementation.}
GRU and LSTM use single-layer recurrences of width $D$ read out at the endpoint;
Mamba-lite is a plain PyTorch selective-state recurrence of the same width.  All
three feed the identical prediction head and loss~\eqref{eq:loss}.  The
Mamba-lite baseline is a controlled selective-recurrence stand-in, not the
optimized official Mamba kernel; we therefore read its results as evidence about
the \emph{format} of recurrence, not as a claim about the strongest possible
state-space implementation.

\section{Full per-environment results}
\label{app:full}

Table~\ref{tab:env-retention-summary} reports, per environment, the slot
writer's mean full/reset/no-state balanced accuracy aggregated over the delay
sweep alongside the strongest recurrent baseline's mean full-memory balanced
accuracy.  Two patterns are visible.  First, the slot controls (reset, no-state)
stay at chance ($\approx0.25$) in every environment, which is what licenses the
retention reading.  Second, the best baseline's full-memory column degrades with
visual structure: navigation decks stay competitive while the manipulation and
scene decks separate sharply as evidence ages.

\begin{table}[h]
\centering
\footnotesize
\caption{Per-environment retention summary (no per-age columns).  Slot columns
are mean full/reset/no-state balanced accuracy over the dense mixed-age delay
sweep (protocol~P1); the ``Best baseline'' column is the strongest recurrent
baseline's mean full-memory balanced accuracy over its evaluated delays
(protocol~P0, \protect\path{outputs/memory_arch_baselines_v1}), with the winning
baseline in parentheses.}
\label{tab:env-retention-summary}
\input{generated_results/env_retention_summary_tabular.tex}
\end{table}

\paragraph{Seed stability.}
Table~\ref{tab:seedpass} reports the number of passing seeds per method on the
age-15 rows.  The slot writer passes all three seeds on every deck; the recurrent
baselines pass intermittently, concentrated on the easier navigation decks.

\begin{table}[h]
\centering
\footnotesize
\caption{Passing seeds (out of 3) per method on age-15 rows.}
\label{tab:seedpass}
\input{generated_results/appendix_seed_pass.tex}
\end{table}

\section{Retrieval versus exposure}
\label{app:retrieval}

The target miner also yields a self-supervised JEPA retrieval statistic
(top-1 match of predicted to true mined latent), which is \emph{not} used for
any paper claim but is informative about the difference between retrieval and
exposure.  Table~\ref{tab:retrieval} reports slot retrieval top-1 by
environment and age.  Retrieval is well above the chance rate expected from the
number of candidates but is not perfectly correlated with readout exposure: some
manipulation decks have moderate retrieval yet strong full-memory exposure,
because the exposed cue class is recoverable even when the exact mined patch is
not the top match.  This is consistent with our central claim that host-visible
\emph{exposure}, not internal retrieval, is the property that matters for a
frozen interface.

\begin{table}[h]
\centering
\footnotesize
\caption{Slot-memory JEPA retrieval top-1 by environment and age
(diagnostic only; not used for gating).}
\label{tab:retrieval}
\input{generated_results/appendix_retrieval.tex}
\end{table}

\section{Full native-use table}
\label{app:native}

Table~\ref{tab:native-full} reports per-environment-age executed success for the
supported decks, with standard deviation over seeds and the recent-only,
random-target, and oracle controls.  The controller receives the
\emph{memory-selected} target rather than the true label, so recent-only and
random targets cannot be repaired downstream; the gain column is full minus the
stronger control.  AntMaze-large/giant and HumanoidMaze-large are omitted because
no audited local low-level controller exists for those bodies; they are
capacity-only in the retention audit and are never counted as native-use
successes.

\begin{table}[h]
\centering
\footnotesize
\caption{Per-environment-age fixed-controller native use on supported decks.
Full is mean\,$\pm$\,std executed success over seeds; gain is full minus the
stronger of recent/random.}
\label{tab:native-full}
\input{generated_results/appendix_native_full.tex}
\end{table}

\section{Mixed-age generalization and the age-router boundary}
\label{app:autoage}

\paragraph{Mixed-age result.}
To test whether the interface is tied to specific training delays, we train the
slot writer with the cue delay sampled continuously (log-uniform) over the legal
range and evaluate held-out episodes at independently drawn continuous delays.
The general per-environment summary is reported in the main text
(Section~\ref{sec:continuous-retention}, Table~\ref{tab:retention-summary}), and
the per-environment delay curves appear in Figure~\ref{fig:env-heatmaps}; we no
longer enumerate a per-age grid.  Full-memory exposure clears the same
fail-closed gate across the swept range while reset and no-state controls remain
at chance, so the delay at which evidence must be retained is not memorized as a
fixed offset: a single interface is delay-robust across the continuous range
rather than at a few enumerated ages.

\paragraph{What is still future work.}
This mixed-age result demonstrates unseen-age \emph{generalization}.  It does not
yet implement a learned explicit age router or an automatic maximum-age search.
The next extension attaches a timestamp to each memory slot and trains a query
network that scores stored slots by content match, timestamp, and confidence,
then selects the top-$k$ slots; evaluation would report the maximum passing age
found by a doubling-and-binary-search protocol.  That answers a different
question (how far back to retrieve, and how far back retrieval remains possible)
than the one audited here (whether old evidence at a given delay is retained and
exposed), and we therefore keep it out of the current claim.

\section{Carrier and loss-component ablations}
\label{app:ablations}

We ablate the two design choices behind the mechanistic claim on the structured
decks (Cube-single, Puzzle-3x3) at age~15.  Table~\ref{tab:abl-slots} varies the
slot count: $S{=}1$ is the single-vector carrier of the target--carrier grid,
and accuracy rises with additional slots, confirming that the slot \emph{set},
not a single compressed vector, carries the multi-part patch-set target.
Table~\ref{tab:abl-loss} removes individual loss terms and swaps in the
streaming writer; the full set objective and the streaming variant retain the
exposure while dropping the contrastive or anti-collapse term degrades it.

\IfFileExists{generated_results/ablation_slots_tabular.tex}{%
\begin{table}[h]
\centering
\footnotesize
\caption{Slot-count (carrier) ablation on structured decks at age~15.}
\label{tab:abl-slots}
\input{generated_results/ablation_slots_tabular.tex}
\end{table}}{}

\IfFileExists{generated_results/ablation_loss_tabular.tex}{%
\begin{table}[h]
\centering
\footnotesize
\caption{Loss-component and streaming ablation on structured decks at age~15.}
\label{tab:abl-loss}
\input{generated_results/ablation_loss_tabular.tex}
\end{table}}{}

\section{Additional analysis notes}
\label{app:notes}

\paragraph{Why the controls are matched at the feature level.}
An earlier and weaker design compares full memory against an unconditioned
classifier.  That comparison is too easy to pass, because class priors and
endpoint pixels can carry substantial signal.  Matching the reset and no-state
controls to the \emph{same} readout, endpoint, and held-out episodes forces any
leaked signal to appear in all three conditions simultaneously, so a leaked deck
cannot pass the gate in Eq.~\eqref{eq:gate}.

\paragraph{Why a set target rather than a frame target.}
A whole-frame latent target can be reconstructed from coarse scene statistics,
which is sufficient for navigation but discards object-level structure.  The
mined patch-\emph{set} target keeps several spatially distributed facts, so the
memory must preserve more than a global summary.  Empirically this is what
separates the manipulation and scene decks as evidence ages
(Tables~\ref{tab:env-retention-summary},~\ref{tab:seedpass}).

\paragraph{Compute.}
Each method sweep is $12$ decks $\times$ $3$ ages $\times$ $3$ seeds $=108$
cells, run across three local GPUs.  The four sweeps (slot, GRU, LSTM,
Mamba-lite) reuse the same rendered caches, so the dominant cost is writer
training rather than data generation.  All figures and tables in this paper are
regenerated in a single pass by \path{scripts/plot_paper_c.py}.
