\bibliographystyle{plainnat}
\begin{thebibliography}{99}
\setlength{\itemsep}{1pt}

\bibitem[Assran et~al.(2023)]{r_jepa}
Mahmoud Assran, Quentin Duval, Ishan Misra, Piotr Bojanowski, Pascal Vincent,
Michael Rabbat, Yann LeCun, and Nicolas Ballas.
\newblock Self-supervised learning from images with a joint-embedding
predictive architecture.
\newblock In \emph{CVPR}, 2023.

\bibitem[Hafner et~al.(2023)]{r_dreamer}
Danijar Hafner, Jurgis Pasukonis, Jimmy Ba, and Timothy Lillicrap.
\newblock Mastering diverse domains through world models.
\newblock \emph{arXiv:2301.04104}, 2023.

\bibitem[Park et~al.(2024)]{r_ogbench}
Seohong Park, Dibya Ghosh, Benjamin Eysenbach, and Sergey Levine.
\newblock OGBench: Benchmarking offline goal-conditioned RL.
\newblock \emph{arXiv preprint}, 2024.

\bibitem[Oord et~al.(2018)]{r_cpc}
Aaron van den Oord, Yazhe Li, and Oriol Vinyals.
\newblock Representation learning with contrastive predictive coding.
\newblock \emph{arXiv:1807.03748}, 2018.

\bibitem[Gu and Dao(2023)]{r_mamba}
Albert Gu and Tri Dao.
\newblock Mamba: Linear-time sequence modeling with selective state spaces.
\newblock \emph{arXiv:2312.00752}, 2023.

\bibitem[Cho et~al.(2014)]{r_gru}
Kyunghyun Cho, Bart van Merrienboer, Caglar Gulcehre, Dzmitry Bahdanau,
Fethi Bougares, Holger Schwenk, and Yoshua Bengio.
\newblock Learning phrase representations using RNN encoder-decoder for
statistical machine translation.
\newblock In \emph{EMNLP}, 2014.

\bibitem[Hochreiter and Schmidhuber(1997)]{r_lstm}
Sepp Hochreiter and Jurgen Schmidhuber.
\newblock Long short-term memory.
\newblock \emph{Neural Computation}, 9(8):1735--1780, 1997.

\bibitem[Vaswani et~al.(2017)]{r_transformer}
Ashish Vaswani, Noam Shazeer, Niki Parmar, Jakob Uszkoreit, Llion Jones,
Aidan Gomez, Lukasz Kaiser, and Illia Polosukhin.
\newblock Attention is all you need.
\newblock In \emph{NeurIPS}, 2017.

\bibitem[Locatello et~al.(2020)]{r_slot_attention}
Francesco Locatello, Dirk Weissenborn, Thomas Unterthiner, Aravindh
Mahendran, Georg Heigold, Jakob Uszkoreit, Alexey Dosovitskiy, and Thomas
Kipf.
\newblock Object-centric learning with slot attention.
\newblock In \emph{NeurIPS}, 2020.

\bibitem[Samsami et~al.(2024)]{r_r2i}
Mohammad Reza Samsami, Artem Zholus, Janarthanan Rajendran, and Sarath
Chandar.
\newblock Mastering memory tasks with world models.
\newblock In \emph{ICLR}, 2024.

\bibitem[Lian et~al.(2025)]{r_loopnav}
Kewei Lian, Shaofei Cai, Yilun Du, and Yitao Liang.
\newblock Toward memory-aided world models: Benchmarking via spatial
consistency.
\newblock \emph{arXiv:2505.22976}, 2025.

\bibitem[Savov et~al.(2025)]{r_statespacediffuser}
Nedko Savov, Naser Kazemi, Deheng Zhang, Danda Pani Paudel, Xi Wang, and Luc
Van Gool.
\newblock StateSpaceDiffuser: Bringing long context to diffusion world models.
\newblock In \emph{NeurIPS}, 2025.

\bibitem[Po et~al.(2025)]{r_lcsvwm}
Ryan Po, Yotam Nitzan, Richard Zhang, Berlin Chen, Tri Dao, Eli Shechtman,
Gordon Wetzstein, and Xun Huang.
\newblock Long-context state-space video world models.
\newblock \emph{arXiv:2505.20171}, 2025.

\bibitem[Stapf et~al.(2026)]{r_memory_experts}
Sebastian Stapf, Pablo Acuaviva Huertos, Aram Davtyan, and Paolo Favaro.
\newblock Composition of memory experts for diffusion world models.
\newblock In \emph{ICLR}, 2026.

\bibitem[Li et~al.(2025)]{r_po_dreamer}
Tianle Li, Peixi Peng, Qingyu Liu, and Luntong Li.
\newblock PO-Dreamer: Memory guided world models for partially observable
reinforcement learning.
\newblock \emph{OpenReview preprint}, 2025.

\bibitem[Eberhard et~al.(2025)]{r_memory_traces}
Onno Eberhard, Michael Muehlebach, and Claire Vernade.
\newblock Partially observable reinforcement learning with memory traces.
\newblock In \emph{ICML}, 2025.

\bibitem[Dao and Gu(2024)]{r_mamba2}
Tri Dao and Albert Gu.
\newblock Transformers are SSMs: Generalized models and efficient algorithms
through structured state space duality.
\newblock In \emph{ICML}, 2024.

\bibitem[Munkhdalai et~al.(2024)]{r_infini_attention}
Tsendsuren Munkhdalai, Manaal Faruqui, and Siddharth Gopal.
\newblock Leave no context behind: Efficient infinite context transformers
with Infini-attention.
\newblock \emph{arXiv:2404.07143}, 2024.

\bibitem[Sun et~al.(2024)]{r_ttt}
Yu Sun, Xinhao Li, Karan Dalal, Jiarui Xu, Arjun Vikram, Genghan Zhang, Yann
Dubois, Xinlei Chen, Xiaolong Wang, Sanmi Koyejo, Tatsunori Hashimoto, and
Carlos Guestrin.
\newblock Learning to (learn at test time): RNNs with expressive hidden
states.
\newblock \emph{arXiv:2407.04620}, 2024.

\bibitem[Behrouz et~al.(2025)]{r_titans}
Ali Behrouz, Peilin Zhong, and Vahab Mirrokni.
\newblock Titans: Learning to memorize at test time.
\newblock \emph{arXiv:2501.00663}, 2025.

\bibitem[Jiang et~al.(2024)]{r_slotssm}
Jindong Jiang, Fei Deng, Gautam Singh, Minseung Lee, and Sungjin Ahn.
\newblock Slot state space models.
\newblock In \emph{NeurIPS}, 2024.

\bibitem[Zhang et~al.(2024)]{r_gsa}
Yu Zhang, Songlin Yang, Ruijie Zhu, Yue Zhang, Leyang Cui, Yiqiao Wang, Bolun
Wang, Freda Shi, Bailin Wang, Wei Bi, Peng Zhou, and Guohong Fu.
\newblock Gated slot attention for efficient linear-time sequence modeling.
\newblock In \emph{NeurIPS}, 2024.

\bibitem[Zhang et~al.(2025)]{r_oc_storm}
Weipu Zhang, Adam Jelley, Trevor McInroe, and Amos Storkey.
\newblock Objects matter: Object-centric world models improve reinforcement
learning in visually complex environments.
\newblock \emph{arXiv:2501.16443}, 2025.

\bibitem[Mosbach et~al.(2025)]{r_sold}
Malte Mosbach, Jan Niklas Ewertz, Angel Villar-Corrales, and Sven Behnke.
\newblock SOLD: Slot object-centric latent dynamics models for relational
manipulation learning from pixels.
\newblock In \emph{ICML}, 2025.

\bibitem[Jeong et~al.(2025)]{r_object_wm_lgm}
Youngjoon Jeong, Junha Chun, Soonwoo Cha, and Taesup Kim.
\newblock Object-centric world model for language-guided manipulation.
\newblock \emph{arXiv:2503.06170}, 2025.

\bibitem[Wang et~al.(2024)]{r_karma}
Zixuan Wang, Bo Yu, Junzhe Zhao, Wenhao Sun, Sai Hou, Shuai Liang, Xing Hu,
Yinhe Han, and Yiming Gan.
\newblock KARMA: Augmenting embodied AI agents with long-and-short term
memory systems.
\newblock \emph{arXiv:2409.14908}, 2024.

\bibitem[Zhu et~al.(2024)]{r_raea}
Yichen Zhu, Zhicai Ou, Xiaofeng Mou, and Jian Tang.
\newblock Retrieval-augmented embodied agents.
\newblock In \emph{CVPR}, 2024.

\bibitem[Gupta et~al.(2025)]{r_memo}
Gunshi Gupta, Karmesh Yadav, Zsolt Kira, Yarin Gal, and Rahaf Aljundi.
\newblock Memo: Training memory-efficient embodied agents with reinforcement
learning.
\newblock \emph{arXiv:2510.19732}, 2025.

\bibitem[Hu et~al.(2025)]{r_3dllm_mem}
Wenbo Hu, Yining Hong, Yanjun Wang, Leison Gao, Zibu Wei, Xingcheng Yao,
Nanyun Peng, Yonatan Bitton, Idan Szpektor, and Kai-Wei Chang.
\newblock 3DLLM-Mem: Long-term spatial-temporal memory for embodied 3D large
language model.
\newblock In \emph{NeurIPS}, 2025.

\bibitem[Yan et~al.(2026)]{r_memory_r1}
Sikuan Yan, Xiufeng Yang, Zuchao Huang, Ercong Nie, Zifeng Ding, Zonggen Li,
Xiaowen Ma, Hinrich Sch{\"u}tze, Volker Tresp, and Yunpu Ma.
\newblock Memory-R1: Enhancing large language model agents to manage and
utilize memories via reinforcement learning.
\newblock In \emph{ACL}, 2026.

\bibitem[Shi et~al.(2026)]{r_rememr1}
Yaorui Shi, Yuxin Chen, Siyuan Wang, Sihang Li, Hengxing Cai, Qi Gu, Xiang
Wang, and An Zhang.
\newblock Look back to reason forward: Revisitable memory for long-context LLM
agents.
\newblock In \emph{ICLR}, 2026.

\bibitem[Hsieh et~al.(2024)]{r_ruler}
Cheng-Ping Hsieh, Simeng Sun, Samuel Kriman, Shantanu Acharya, Dima Rekesh,
Fei Jia, Yang Zhang, and Boris Ginsburg.
\newblock RULER: What's the real context size of your long-context language
models?
\newblock In \emph{COLM}, 2024.

\bibitem[Wu et~al.(2025)]{r_longmemeval}
Di Wu, Hongwei Wang, Wenhao Yu, Yuwei Zhang, Kai-Wei Chang, and Dong Yu.
\newblock LongMemEval: Benchmarking chat assistants on long-term interactive
memory.
\newblock In \emph{ICLR}, 2025.

\bibitem[LeWorldModel Team(2026)]{r_lewm}
LeWorldModel Team.
\newblock LeWorldModel: Stable end-to-end joint-embedding predictive
architecture from pixels.
\newblock \emph{arXiv:2603.19312}, 2026.

\bibitem[Anonymous(2025)]{r_onmemory}
Anonymous.
\newblock On memory: A comparison of memory mechanisms in world models.
\newblock \emph{arXiv:2512.06983}, 2025.

\bibitem[Anonymous(2026)]{r_causaljepa}
Anonymous.
\newblock Causal-JEPA: Learning world models through object-level latent
masking.
\newblock \emph{arXiv:2602.11389}, 2026.

\bibitem[Anonymous(2026)]{r_slotmemory}
Anonymous.
\newblock SlotMemory: Object-centric KV memory for streaming long-video
generation.
\newblock \emph{arXiv:2605.31033}, 2026.

\end{thebibliography}
