\section{Artifact map}

The paper is generated from current local artifacts rather than hand-entered
plots.  The figure-generation script is
\path{scripts/plot_paper_b.py}.  It writes figures to
\path{paper_b/figures/} and a JSON snapshot to
\path{paper_b/generated_results/result_snapshot.json}.

\begin{table}[H]
\centering
\footnotesize
\caption{Primary local result sources used by this paper.}
\begin{tabularx}{\linewidth}{lY}
\toprule
Claim & Local source\\
\midrule
PushT checkpointed downstream use
  & \path{outputs/pusht_checkpointed_downstream_use_v1/summary.json}\\
PointMaze carrier grid
  & \path{outputs/dinowm_pointmaze_wave3/formal/carrier_summary.json}\\
PointMaze external use
  & \path{outputs/dinowm_pointmaze_wave3/formal/external_use_summary.json}\\
Wall PCA-logistic confirmation
  & \path{outputs/dinowm_wall_audit_v1/stage_h_logistic_readout/summary.json}\\
Wall ridge screen
  & \path{outputs/dinowm_wall_audit_v1/stage_h_carriers/summary.json}\\
OGBench admission bridge
  & \path{outputs/ogbench_mesmem_admission_v1/summary_all.json}\\
OGBench feature-host capacity
  & \path{outputs/ogbench_feature_host_stage_v1/summary.json}\\
OGBench native-use success
  & \path{outputs/ogbench_native_use_stage_v1/summary.json}\\
OGBench repaired all-env native-use success
  & \path{outputs/native_use_repaired_combined_v1/summary.json}\\
Final non-manual OGBench patch-set JEPA
  & \path{outputs/random_patchset_view_color_jepa_final_v1/summary.json}\\
\bottomrule
\end{tabularx}
\end{table}

\input{generated_results/native_use_repaired_allenv_auto.tex}
\input{generated_results/nonmanual_breadth_auto.tex}

\section{Detailed claim ledger}

\begin{table}[H]
\centering
\footnotesize
\caption{Expanded ledger corresponding to Figure~\ref{fig:claim-ledger}.  The
main paper uses the visual ledger; this table records the detailed boundary for
each row.}
\begin{tabularx}{\linewidth}{lYcccY}
\toprule
Environment & Host / task & Retention & Exposure & Use & Boundary\\
\midrule
PushT & DINO-WM and LeWM, six-way visual binding, age 15
  & \Pass & \Pass & \Pass
  & Cross-host use gate passes; host-native banks prevent a row-matched causal
    comparison between host families.\\
PointMaze & DINO-WM, four-goal transient cue
  & \Pass & \Pass & \Pass
  & Strong external consumer result; not native planner memory.\\
Wall & DINO-WM, four-position transient wall cue
  & \Pass & mixed & \NA
  & Carrier-prior memory remains high; host-output exposure confirms only at
    short cue age.\\
OGBench & Seven admitted decks; repaired fixed-controller native use plus
  two-deck non-manual patch-set JEPA
  & \Pass & \Pass & \Pass
  & Admission passes across seven decks.  The repaired native-use sweep scores
    24/36 env-age rows under fixed controllers, and the non-manual patch-set
    JEPA stage passes all 30 registered PointMaze-large/Cube-single retention
    cells.  No native OGBench planner is claimed.\\
\bottomrule
\end{tabularx}
\end{table}

\section{Quantitative result summary}

\paragraph{PushT checkpointed use.}
At age 15, both frozen host families support the same qualitative conclusion:
full memory separates from reset and no-state controls in host readout and
executed success.  DINO-WM full memory reaches balanced accuracy 0.988 and
executed success 0.972, while reset/no-state execution remains near the
six-way uninformed regime.  LeWM full memory reaches balanced accuracy 0.920
and executed success 0.926 with the same control pattern.

\begin{table}[H]
\centering
\footnotesize
\caption{PushT binding use summary.}
\begin{tabular}{lccc}
\toprule
Host & Full execution & Reset execution & No-state execution\\
\midrule
DINO-WM & 0.972 & 0.167 & 0.168\\
LeWM    & 0.926 & 0.156 & 0.151\\
\bottomrule
\end{tabular}
\end{table}

\paragraph{PointMaze external use.}
The fixed consumer preserves the carrier ordering in navigation execution.  No
state remains close to random-goal behavior; state-space and fixed-trust are
the strongest arms.

\begin{table}[H]
\centering
\footnotesize
\caption{PointMaze external-use summary.}
\begin{tabular}{lcc}
\toprule
Arm & Goal/read accuracy & Executed success\\
\midrule
No state & 0.250 & 0.239\\
GRU & --- & 0.302\\
LSTM & --- & 0.484\\
State-space & 0.760 & 0.745\\
Fixed-trust & 0.866 & 0.775\\
\bottomrule
\end{tabular}
\end{table}

\paragraph{Wall readout note.}
The Wall carrier grid was first screened with a deterministic ridge readout.
That screen suggested fixed-trust might clear host-output exposure at ages 4
and 8.  The paper uses the stricter confirmation run instead:
StandardScaler, PCA(256), and logistic regression fit only on the training
split.  Under this confirmation fixed-trust clears only age 4, while
state-space does not clear any age.  This is why Wall is described as exposure
failure localization rather than a broad success result.

\begin{table}[H]
\centering
\footnotesize
\caption{Wall confirmation: carrier prior remains high while host-output
exposure decays.}
\begin{tabular}{llccc}
\toprule
Arm & Readout & Age 4 & Age 8 & Age 15\\
\midrule
Fixed-trust & carrier prior & 1.000 & 1.000 & 1.000\\
Fixed-trust & host output & 0.929 & 0.446 & 0.297\\
State-space & carrier prior & 1.000 & 0.995 & 0.989\\
State-space & host output & 0.565 & 0.301 & 0.272\\
\bottomrule
\end{tabular}
\end{table}

\section{OGBench claim boundary}

The OGBench admission bridge checks only whether a controlled cue deck is
valid: cue-time encoding must be high, endpoint/action/state shortcuts must be
near chance, and counterfactual masks must not leak post-cue evidence.  It
does not train a frozen OGBench world model and does not run downstream
execution.

The follow-up feature-host stage is one rung stronger but still bounded.  It
uses admitted decks, DINOv2 pooled patch features as a frozen feature
interface, and a sidecar that carries the old cue feature before writing a
residual into the endpoint feature.  The writer loss is self-supervised against
the cue feature, while labels are used only for the post-hoc readout.

The native-use stage then asks whether the selected label changes final
environment success.  Non-teleport PointMaze uses a BFS waypoint controller
over native point-mass actions.  Cube variants use the OGBench
CubeMarkovOracle with selected-label target metadata, Puzzle uses a lights-out
solve with the button oracle, and Scene composes button, drawer, window, and
cube Markov oracles.  The repaired sweep scores 24/36 env-age rows; the
PointMaze-teleport controller gate remains below threshold, and
AntMaze/HumanoidMaze remain unscored without local low-level controllers.
These are fixed-controller use checks; they are not native OGBench world-model
planning.

The final non-manual stage then removes the explicit cue-feature handoff on
PointMaze-large and Cube-single.  It mines salient target frames and patch
sets without cue labels or cue-layout knowledge, predicts fixed generic
color/texture patch latents through compact slots, and evaluates the learned
state only after training.  This certifies autonomous old-evidence retention
for the two core render-stage decks, but not yet broad OGBench-wide
generalization or native planner memory.

\begin{table}[H]
\centering
\footnotesize
\caption{OGBench admission summary.  All rows pass cue-time readability,
shortcut, and mask checks; all memory/use columns are intentionally unclaimed.}
\begin{tabularx}{\linewidth}{lYccc}
\toprule
Deck & Family & Cue read & Max shortcut & Mask audit\\
\midrule
PointMaze-large-navigate & navigation & 1.000 & 0.250 & pass\\
AntMaze-large-navigate & locomotion & 1.000 & 0.250 & pass\\
HumanoidMaze-large-navigate & high-DoF locomotion & 1.000 & 0.250 & pass\\
Cube-single-play & object manipulation & 1.000 & 0.250 & pass\\
Cube-double-play & object manipulation & 1.000 & 0.250 & pass\\
Scene-play & multi-object scene & 1.000 & 0.250 & pass\\
Puzzle-3x3-play & combinatorial puzzle & 1.000 & 0.250 & pass\\
\bottomrule
\end{tabularx}
\end{table}

\begin{table}[H]
\centering
\footnotesize
\caption{OGBench feature-host capacity summary.  Gate: full host-output
balanced accuracy at least 0.750, reset and no-state controls at most 0.300.
All rows use 200 train bases, 80 validation bases, and five seeds.}
\begin{tabular}{lcccc}
\toprule
Deck & Age & Seeds passing & Full & Reset/no-state\\
\midrule
AntMaze-large-navigate & 4  & 5/5 & 1.000 & 0.250 / 0.250\\
AntMaze-large-navigate & 8  & 5/5 & 1.000 & 0.250 / 0.250\\
AntMaze-large-navigate & 15 & 5/5 & 1.000 & 0.250 / 0.250\\
Cube-single-play       & 4  & 5/5 & 1.000 & 0.250 / 0.250\\
Cube-single-play       & 8  & 5/5 & 1.000 & 0.250 / 0.250\\
Cube-single-play       & 15 & 5/5 & 1.000 & 0.250 / 0.250\\
\bottomrule
\end{tabular}
\end{table}

Table~\ref{tab:native-use-repaired-allenv} reports the repaired all-env
native-use sweep.  It subsumes the earlier PointMaze-large/Cube-single slice
and keeps controller-gate failures and unavailable locomotion controllers as
explicit scope limits.

\begin{table}[H]
\centering
\footnotesize
\caption{Final non-manual OGBench patch-set JEPA summary.  Labels are used
only for post-hoc audit; training uses no cue labels, cue crops, or key-frame
annotations.}
\begin{tabular}{lccccc}
\toprule
Deck & Age & Seeds passing & Full & Reset & Recent-only\\
\midrule
PointMaze-large-navigate & 4  & 5/5 & 1.000 & 0.251 & 0.255\\
PointMaze-large-navigate & 8  & 5/5 & 0.994 & 0.266 & 0.250\\
PointMaze-large-navigate & 15 & 5/5 & 0.983 & 0.251 & 0.252\\
Cube-single-play         & 4  & 5/5 & 1.000 & 0.240 & 0.257\\
Cube-single-play         & 8  & 5/5 & 0.990 & 0.223 & 0.254\\
Cube-single-play         & 15 & 5/5 & 0.921 & 0.247 & 0.246\\
\bottomrule
\end{tabular}
\end{table}
