\begin{thebibliography}{99}\small

\bibitem[Belinkov(2022)]{r_belinkov}
Yonatan Belinkov.
\newblock Probing classifiers: Promises, shortcomings, and advances.
\newblock \emph{Computational Linguistics}, 48(1), 2022.

\bibitem[Deng et al.(2023)]{r_s4wm}
Fei Deng, Junyoung Park, and Sungjin Ahn.
\newblock Facing off world model backbones: RNNs, transformers, and S4.
\newblock \emph{NeurIPS}, 2023.

\bibitem[Gao \& Xu(2026)]{r_fastlewm}
Yuntian Gao and Xiangyu Xu.
\newblock Fast LeWorldModel.
\newblock arXiv:2606.26217, 2026.

\bibitem[Garcin et al.(2026)]{r_persist}
Samuel Garcin, Thomas Walker, Steven McDonagh, Tim Pearce, Hakan Bilen, Tianyu He, Kaixin Wang, and Jiang Bian.
\newblock Beyond pixel histories: World models with persistent 3D state.
\newblock arXiv:2603.03482, 2026.

\bibitem[Hafner et al.(2025)]{r_dreamerv3}
Danijar Hafner, Jurgis Pasukonis, Jimmy Ba, and Timothy Lillicrap.
\newblock Mastering diverse control tasks through world models.
\newblock \emph{Nature}, 640:647--653, 2025.

\bibitem[Laird \& Clark(2025)]{r_onmemory}
Eli J. Laird and Corey Clark.
\newblock On memory: A comparison of memory mechanisms in world models.
\newblock arXiv:2512.06983, 2025.

\bibitem[Li et al.(2026)]{r_rcaux}
Wenyuan Li, Guang Li, Keisuke Maeda, Takahiro Ogawa, and Miki Haseyama.
\newblock Predictive but not plannable: RC-aux for latent world models.
\newblock arXiv:2605.07278, 2026.

\bibitem[Lu et al.(2026)]{r_statecore}
Jinpeng Lu, Dexu Zhu, Haoyuan Shi, Linghan Cai, Guo Tang, Yinda Chen, Jie Cao, Duyu Tang, Yi Zhang, Yong Dai, and Xiaozhu Ju.
\newblock Current world models lack a persistent state core.
\newblock arXiv:2606.20545, 2026.

\bibitem[Maes et al.(2026)]{r_lewm}
Lucas Maes, Quentin Le Lidec, Damien Scieur, Yann LeCun, and Randall Balestriero.
\newblock LeWorldModel: Stable end-to-end joint-embedding predictive architecture from pixels.
\newblock arXiv:2603.19312, 2026.

\bibitem[Park et al.(2025)]{r_ogbench}
Seohong Park, Kevin Frans, Benjamin Eysenbach, and Sergey Levine.
\newblock OGBench: Benchmarking offline goal-conditioned RL.
\newblock \emph{ICLR}, 2025.

\bibitem[Ravichander et al.(2021)]{r_ravich}
Abhilasha Ravichander, Yonatan Belinkov, and Eduard Hovy.
\newblock Probing the probing paradigm: Does probing accuracy entail task relevance?
\newblock \emph{EACL}, 2021.

\bibitem[Samsami et al.(2024)]{r_r2i}
Mohammad Reza Samsami, Artem Zholus, Janarthanan Rajendran, and Sarath Chandar.
\newblock Mastering memory tasks with world models.
\newblock \emph{ICLR}, 2024.

\bibitem[Wang et al.(2026)]{r_dimwam}
Kai Wang, Zhaopeng Gu, Yixiang Chen, Yuan Xu, Qisen Ma, Peng Su, Zhaowen Li, Yan Huang, and Liang Wang.
\newblock DIM-WAM: World-action modeling with diverse historical event memory.
\newblock arXiv:2606.27677, 2026.

\bibitem[Yang et al.(2026)]{r_memorywam}
Sizhe Yang, Juncheng Mu, Tianming Wei, Chenhao Lu, Xiaofan Li, Linning Xu, Zhengrong Xue, Zhecheng Yuan, Dahua Lin, Jiangmiao Pang, and Huazhe Xu.
\newblock MemoryWAM: Efficient world action modeling with persistent memory.
\newblock arXiv:2606.20562, 2026.

\bibitem[Zheng et al.(2026)]{r_memworld}
Zirui Zheng, Jiaqian Yu, Xiongfeng Peng, Jun Shi, Mingyi Li, Chao Zhang, Weiming Li, Dong Wang, Huchuan Lu, and Xu Jia.
\newblock Mem-World: Memory-augmented action-conditioned world models for persistent robot manipulation.
\newblock arXiv:2606.18960, 2026.

\bibitem[Zhou et al.(2025)]{r_dinowm}
Gaoyue Zhou, Hengkai Pan, Yann LeCun, and Lerrel Pinto.
\newblock DINO-WM: World models on pre-trained visual features enable zero-shot planning.
\newblock \emph{ICML}, 2025.

\end{thebibliography}
