\begin{thebibliography}{99}\small
\bibitem[Assran et al.(2025)]{ref4} Assran et al. \emph{V-JEPA 2: Self-Supervised Video Models Enable Understanding, Prediction and Planning.} 2025 (arXiv:2506.09985).
\bibitem[Balestriero \& LeCun(2025)]{ref16} Balestriero, LeCun. \emph{LeJEPA: Provable and Scalable Self-Supervised Learning Without the Heuristics.} 2025 (arXiv:2511.08544).
\bibitem[Bardes et al.(2022)]{ref17} Bardes, Ponce, LeCun. \emph{VICReg: Variance-Invariance-Covariance Regularization for Self-Supervised Learning.} ICLR 2022.
\bibitem[Becker et al.(2019)]{ref12} Becker et al. \emph{Recurrent Kalman Networks: Factorized Inference in High-Dimensional Deep Feature Spaces.} ICML 2019.
\bibitem[Cherepanov et al.(2026)]{ref14} Cherepanov, Kovalev, Panov. \emph{ELMUR: External Layer Memory with Update/Rewrite for Long-Horizon RL Problems.} ICLR 2026.
\bibitem[Deng et al.(2023)]{ref9} Deng, Park, Ahn. \emph{Facing Off World Model Backbones: RNNs, Transformers, and S4.} NeurIPS 2023.
\bibitem[Ghaemi et al.(2025)]{ref2} Ghaemi, Muller, Bakhtiari. \emph{seq-JEPA: Autoregressive Predictive Learning of Invariant-Equivariant World Models.} NeurIPS 2025.
\bibitem[Hafner et al.(2020)]{ref7} Hafner et al. \emph{Dream to Control: Learning Behaviors by Latent Imagination.} ICLR 2020.
\bibitem[Hafner et al.(2019)]{ref6} Hafner et al. \emph{Learning Latent Dynamics for Planning from Pixels.} ICML 2019.
\bibitem[Hafner et al.(2025)]{ref8} Hafner et al. \emph{Mastering Diverse Control Tasks through World Models.} Nature, 2025.
\bibitem[Lillemark et al.(2026)]{ref15} Lillemark et al. \emph{Flow Equivariant World Models: Structured Memory for Dynamic Environments.} ICML 2026 (arXiv:2601.01075).
\bibitem[Maes et al.(2026)]{ref1} Maes, Le Lidec, Scieur, LeCun, Balestriero. \emph{LeWorldModel: Stable End-to-End Joint-Embedding Predictive Architecture from Pixels.} 2026 (arXiv:2603.19312).
\bibitem[Samsami et al.(2024)]{ref10} Samsami et al. \emph{Mastering Memory Tasks with World Models.} ICLR 2024.
\bibitem[Schölkopf et al.(2021)]{ref5} Schölkopf et al. \emph{Toward Causal Representation Learning.} Proceedings of the IEEE, 2021.
\bibitem[Shaj et al.(2021)]{ref13} Shaj et al. \emph{Action-Conditional Recurrent Kalman Networks for Forward and Inverse Dynamics Learning.} CoRL 2020, PMLR 155, 2021.
\bibitem[Shaj et al.(2023)]{ref11} Shaj et al. \emph{Multi Time Scale World Models.} NeurIPS 2023.
\bibitem[Tassa et al.(2018)]{ref18} Tassa et al. \emph{DeepMind Control Suite.} 2018 (arXiv:1801.00690).
\bibitem[Zhou et al.(2025)]{ref3} Zhou, Pan, LeCun, Pinto. \emph{DINO-WM: World Models on Pre-trained Visual Features Enable Zero-Shot Planning.} ICML 2025.
\end{thebibliography}
